Assessing spatial correlations in pulsar timing arrays with the noise-marginalized optimal statistic

### 2018-03-19 manuscript/manuscript.tex
updated abstract

\begin{abstract}
Supermassive black hole binaries (SMBHBs) are predicted to form a 
high-redshift cosmological population of low-frequency gravitational wave sources 
which added together produce a stochastic gravitational wave background (GWB) 
that can be observed by pulsar timing arrays (PTAs). 
Comparing the actual and predicted times-of-arrival (TOAs) of radio pulses beamed by 
millisecond pulsars allows us to search for and place limits on the stochastic background. 
While most estimating of GWB significance is done via Bayesian analysis, 
here we use a frequentist estimator called the noise-marginalized optimal statistic 
to assess the significance of a GWB present in simulated PTA data. We find \ki{complete}

Test travis...

>>>>

\begin{abstract}
Supermassive black hole binaries (SMBHBs) are predicted to form a 
high-redshift cosmological population of low-frequency gravitational wave (GW) sources, 
which added together produce a stochastic gravitational wave background (GWB). 
Pulsar timing arrays (PTAs) can observe this signal by looking for correlations in the 
times of arrival (TOAs) of millisecond pulsars (MSPs). 
In this paper, we introduce an improved frequentist estimator called the noise-marginalized optimal statistic, 
which can be used to assess the significance of a GWB present in PTA data. 
We find \ki{complete}
